\bf A Concise Survey on Statistical Analysis in Bike Lane Research

### 2023-11-11 Manuscript/Manuscript.tex
added more to background section

@@

The Connecticut State government describes the common facility types used to accommodate cyclists as Shared Roadways, Wide Curb-lanes, Bicycle Lanes and Multi-use Paths.

>>>>

In order to understand the research into bike lanes, these topics should be understood.

@@

The Connecticut State government describes the common facility types used to accommodate cyclists as Shared Roadways, Wide Curb-lanes, Bicycle Lanes and Multi-use Paths.\par
Shared roadways are where bicycle and automobile travel are allowed, all streets and roads other than controlled highways, are in this category. They do not provide any added protection to cyclists, but a street's designation as shared roadway indicates to cyclists that there are advantages to using the route over alternatives. Wide curb lanes are still for sharing between bicycle and motorized traffic, but they provide more distance between bicyclists and vehicles and protection from high traffic speeds. They are created by widening roadways or narrowing traffic lanes, or both.\par 
The category of bicycle lanes is defined as painted and signed lanes on the shoulder of streets, to improve conditions for bicyclists and to protect them from traffic volume and speed. Being designated as a bike lane street, means that more "pavements surface improvements, stronger sweeping programs, special signal facilities, etc" occur on them to increase safety and comfort for cyclists. \par
The last level of cycling infrastructure is multi-use paths, on which cyclists have exclusive rights-of-way and don't cross The flow of automobiles more than necessary. These can be both recreational opportunities or high=speed commuter routes for cyclists. \par
The research in this survey focuses on the infrastructure of bicycle lanes, and whether they are sufficient to increase the propensities of people to cycle, and their safety while they are cycling.
